---
title: "get today's covid19 data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get today's covid19 data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

You can get today's world covid19 data to use this library

```{r setup}
library(covid19today)
```

## About Function

You can get **get_data()** function to get today's covid19 data

there's 2 option of data

- country: country data is consist of all country's covid19 stat
- continent: you can see the covid19 data of all continent

```{r, eval=FALSE}
data <- get_data("country")
```

If you want to extract data to use other language or Tools,
you can export 5 format of Tools

1. .csv file
```{r, eval=FALSE}
get_data_csv("country")
```

2. .xlsx file(Excel)
```{r, eval=FALSE}
get_data_excel("continent")
```

3. .sav file(SPSS)
```{r, eval=FALSE}
get_data_spss("country")
```

4. .xpt file(SAS)
```{r, eval=FALSE}
get_data_sas("continent")
```

5. .dta file(Stata)
```{r, eval=FALSE}
get_data_stata("country")
```
